\bf What is the Best Way to Display Two Time Series to Read Association?

### 2017-01-02 Confirmation/VB.tex
Xmas break updates

\documentclass{article}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[]{algorithm2e}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage{afterpage}
\usepackage{bbm}
\numberwithin{equation}{section}

\begin{document}

@@

\begin{figure}[hb]
<<klnorm, echo = FALSE, fig.width = 6, fig.height = 2>>=
library(ggplot2)
xseq = seq(-0.5, 1, 0.01)
w1 = dnorm(xseq, 0, 0.1)
w2 = dnorm(xseq, 0.5, 0.1)
ggplot() + geom_line(data=NULL, aes(x=xseq, y = w1), colour = "red") + geom_line(data=NULL, aes(x=xseq, y = w2), colour = "green") + labs(x="Support", y = "Density") + theme_bw()
@
\caption{Red: A Normal(0, 0.1) distribution. Green: A Normal(0.5, 0.1) distribution.}
\end{figure}

@@

\begin{figure}
\label{AR2MCMC}
\centering
<<AR2MCMC, echo = FALSE, fig.height = 4, fig.width = 4>>=
library(ggplot2)
library(gridExtra)
draws <- read.csv("AR2thin.csv")[,-1]
colnames(draws) = c("Phi1", "Phi2", "SigmaSquared")
m1 <- ggplot(data=draws, aes(x=Phi1)) + geom_density() + theme_bw() + ylab(NULL) + xlab(expression(phi[1]))
m2 <-  ggplot(data=draws, aes(x=Phi2)) + geom_density() + theme_bw() + ylab(NULL) + xlab(expression(phi[2]))
m3 <-  ggplot(data=draws, aes(x=SigmaSquared)) + geom_density() + theme_bw() + ylab(NULL) + xlab(expression(sigma^2))
j1 <- ggplot(data=draws, aes(x=Phi1, y = Phi2)) + geom_density2d() + theme_bw() + xlab(expression(phi[1])) + ylab(expression(phi[2]))
j2 <- ggplot(data=draws, aes(x=Phi1, y = SigmaSquared)) + geom_density2d() + theme_bw() + xlab(expression(phi[1])) + ylab(expression(sigma^2))
j3 <- ggplot(data=draws, aes(x=Phi2, y = SigmaSquared)) + geom_density2d() + theme_bw() + xlab(expression(phi[2])) + ylab(expression(sigma^2))
grid.arrange(m1, m2, m3, j1, j2, j3, ncol = 3)
@
\caption{Marginal and bivariate density plots of the MCMC draws. 100,000 draws per parameter were sampled from (\ref{AR2}) via Gibbs MCMC then reduced to 4000 each. Note the strong dependence between the two $\phi$ parameters.}
\end{figure}

@@

\begin{table}
\centering
\label{AR2results}
<<AR2summary, echo = FALSE>>=
library(knitr)
summary = matrix(c(0.83, 0.10, 0.04, 0, 0.05, 50, 79.7, -77.7, "1.3 x 10^{-6}", 
                 0.63, 0.27, 0.09, -0.12, 0.05, 45.6, 81.4, -78.3, 51.1, 
                 0.78, 0.15, 0.1, -0.09, 0.05, 49.3, 78, -76.7, 4.0,
                 0.77, 0.15, 0.09, -0.09, 0.05, 48.5, 77.6, -76.9, 1.3), byrow = TRUE, ncol = 9)
colnames(summary) = c("mu1", "mu2", "L11", "L21", "L22", "alpha", "beta", "ELBO", "Runtime (seconds)")
rownames(summary) = c("Mean Field", "SGA", "SGA-RP", "SGA-CV")
kable(summary)
@
\caption{Parameter estimates, maximised ELBO and runtime of all Variational Bayes algorithms.}
\end{table}

>>>>

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{natbib}
\usepackage{color}
\usepackage[dvipsnames,svgnames*]{xcolor}
\usepackage{array}
\usepackage[hidelinks]{hyperref}
\usepackage[font=small,skip=5pt]{caption}
\usepackage[aboveskip=2pt]{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{dsfont}
\usepackage[]{algorithm2e}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{url}
\usepackage{ulem}
\usepackage{afterpage}
\usepackage{bbm}
\numberwithin{equation}{section}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

@@

\begin{figure}[hb]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/klnorm-1}

\end{knitrout}
\caption{Red: A Normal(0, 0.1) distribution. Green: A Normal(0.5, 0.1) distribution.}
\end{figure}

@@

\begin{figure}
\label{AR2MCMC}
\centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/AR2MCMC-1}

\end{knitrout}
\caption{Marginal and bivariate density plots of the MCMC draws. 100,000 draws per parameter were sampled from (\ref{AR2}) via Gibbs MCMC then reduced to 4000 each. Note the strong dependence between the two $\phi$ parameters.}
\end{figure}

@@

\begin{table}
\centering
\label{AR2results}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{tabular}{l|l|l|l|l|l|l|l|l|l}
\hline
  & mu1 & mu2 & L11 & L21 & L22 & alpha & beta & ELBO & Runtime (seconds)\\
\hline
Mean Field & 0.83 & 0.1 & 0.04 & 0 & 0.05 & 50 & 79.7 & -77.7 & 1.3 x 10\textasciicircum{}\{-6\}\\
\hline
SGA & 0.63 & 0.27 & 0.09 & -0.12 & 0.05 & 45.6 & 81.4 & -78.3 & 51.1\\
\hline
SGA-RP & 0.78 & 0.15 & 0.1 & -0.09 & 0.05 & 49.3 & 78 & -76.7 & 4\\
\hline
SGA-CV & 0.77 & 0.15 & 0.09 & -0.09 & 0.05 & 48.5 & 77.6 & -76.9 & 1.3\\
\hline
\end{tabular}

\end{knitrout}
\caption{Parameter estimates, maximised ELBO and runtime of all Variational Bayes algorithms.}
\end{table}
